Network segregation, Social Isolation and Preference for Redistribution across societies

### 2023-09-19 paper.Rmd
ajuste modelos

---
title: "Lorem ipsum dolor sit amet"
css: "input/css/custom.css" # custom CSS para html
linestretch: '1.5'          # interlineado 
link-citations: yes         # citas linkeadas
author:
- name: Duke A Caboom
  affiliation: University of Tuktoyaktuk
  email: dtholmes@mail.ubc.ca
  number: 1
- name: Justin d'Ottawa
  affiliation: University of Ottawa
  number: 2
- name: Pedro Torres
  number: 1,2 
# Nota: Autores que comparten filiacion, poner el mismo number y declarar filiación una sola vez.  
abstract: "Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do *eiusmod tempor* incididunt ut labore et dolore magna aliqua. Ut enimad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat."
output:
  bookdown::pdf_document2:
    template: null
    toc: false
    keep_tex: false
    pandoc_args:
      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
  bookdown::html_document2:
    number_sections: false
linkcolor: blue                         # enlaces y citas en color azul
bibliography: input/bib/library.bib     # bibliografia en bibtex
editor_options:
  chunk_output_type: console            # en RStudio, mostrar output en consola
geometry: "left=2cm,right=2cm,top=3cm,bottom=3cm" # márgenes de página
header-includes:
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
---

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")  #si falta pacman, instalar
if (!require("tinytex")) install.packages("tinytex")#si falta tinytex, instalar
pacman::p_load(knitr, kableExtra, dplyr, ggplot2,sjmisc,texreg) # librerias
knitr::opts_chunk$set(warning = FALSE,  # mensaje de warning
                      message = FALSE,  # mensajes/avisos de librerias  
                      cache = FALSE,    # cache de los chunks,usar analisis pesados
                      out.width = '85%',# largo de imagen en %
                      fig.pos= "H",     # posicion figuras H = HERE
                      echo = FALSE      # incluir chunk en output
                      )
options(scipen=999) # notacion cientifica
rm(list=ls())       # limpiar workspace
options(knitr.kable.NA = '') # NA en kable = ''

table_format = if(is_html_output()) { # Usar en argumento "format=" de kable
  "html"
} else if(is_latex_output()) {
  "latex"
}

fwidth = if(is_html_output()) { #Usar en argumento "full_width" de kableExtra
  T
} else if(is_latex_output()) {
  F
}
```

@@

- class x network segregation

  - the influence of homogeneity is positive among the working and intermediate classes, and negative among the upper class

@@

>>>>

---
title: "Network segregation, Social Isolation and Preference for Redistribution across societies"
css: "input/css/custom.css" # custom CSS para html
linestretch: '1.5'          # interlineado 
link-citations: yes         # citas linkeadas
author:
# - name: Julio Iturra-Sanhueza
#   affiliation: University of Bremen
#   email: jiturra@uni-bremen.de
#   number: 1
# - name: Justin d'Ottawa
#   affiliation: University of Ottawa
#   number: 2
# - name: Pedro Torres
#   number: 1,2 
# Nota: Autores que comparten filiacion, poner el mismo number y declarar filiación una sola vez.  
# abstract: "Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do *eiusmod tempor* incididunt ut labore et dolore magna aliqua. Ut enimad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat."
output:
  bookdown::html_document2:
    number_sections: false
  bookdown::pdf_document2:
    template: null
    toc: false
    keep_tex: false
    pandoc_args:
      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
linkcolor: blue                         # enlaces y citas en color azul
bibliography: input/bib/library.bib     # bibliografia en bibtex
editor_options:
  chunk_output_type: console            # en RStudio, mostrar output en consola
geometry: "left=2cm,right=2cm,top=3cm,bottom=3cm" # márgenes de página
header-includes:
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
---

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")  #si falta pacman, instalar
if (!require("tinytex")) install.packages("tinytex")#si falta tinytex, instalar
pacman::p_load(knitr, kableExtra, dplyr, ggplot2,sjmisc,texreg) # librerias
knitr::opts_chunk$set(warning = FALSE,  # mensaje de warning
                      message = FALSE,  # mensajes/avisos de librerias  
                      cache = FALSE,    # cache de los chunks,usar analisis pesados
                      out.width = '85%',# largo de imagen en %
                      fig.pos= "H",     # posicion figuras H = HERE
                      echo = FALSE      # incluir chunk en output
                      )
options(scipen=999) # notacion cientifica
rm(list=ls())       # limpiar workspace
options(knitr.kable.NA = '') # NA en kable = ''
```

@@

- class x network segregation 
- the influence of homogeneity is positive among the working and intermediate classes, and negative among the upper class

@@

The structure of the social network provide access to social resources. On the one hand, contacts can be translated into resources, access to the life of others that could provide information and life opportunities.

- stratified access to resources
- class and networks (focus of this paper)

Some research has connected social capital with economic rational dimension, while others have conected it to more value-driven or moralistic dimension

Both assume direct effects,but other literature such as Otero et al has suggested that experiences might vary across social classes.

For example, we trust other people because we know about them (connected)

<!-- Across all countries, a nurse (41.2%) and a schoolteacher (39.6%) are mentioned the most often and a human resource manager (19.2%) and a lawyer (22.2%) the least often. Considering the scope of the network, Suriname (42%), the United States (41.4%), and Iceland (41.3%) are the countries in which respondents are connected to the widest array of occupations, while Thailand (13.2%), Japan (15%), and Taiwan (18.9%) represent the other end. The social network thus is larger and more diverse in the former countries -->

# Results

## Descriptive

```{r redistribution}
# x country

```

```{r homogeneity}
# x country
```

```{r macro}

```

- class x homogeneity (3 plots)
- homogeneity x redistribution (1 plot)
- perceived isolation x redistribution (1 plot)
- homogeneity x perceived isolation (1 plot)

## Multivariate

```{r,results='asis', cache=T}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven)
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
                          as.factor = T,
                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass,
                        incomepcap,
                        gini_disp,
                        gini_mkt,
                        rgdpna,
                        edyears,
                        female,
                        agenum,
                        country2,pi_isola,
                        # union,
                        # labst,
                        # WEIGHT
                        ) %>% 
  mutate(logrgdpna=log(rgdpna)) %>%
  # filter(!country2 %in% c("Turkey","Estonia")) %>% 
  na.omit()

# lineal
base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
homclass <- lmer(redist~1 + female+agenum + homclass +(1|country2),data=dfreg)
class <- lmer(redist~1 +female+agenum + class3+(1|country2),data=dfreg)
full <- lmer(redist~1 +female+agenum + class3 +edyears+homclass+incomepcap+(1|country2),data=dfreg)
# Interactions segregation x class
full_int1 <- lmer(redist~1 +female+agenum + edyears + incomepcap + homclass*class3 +(1|country2),data=dfreg)
models <- list(homclass,class,full,full_int1)

cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
omitcoef <- "(Intercept)|(agenum)|(female)|(incomepcap)|(edyears)|(logrgdpna)"
coefname <- c("Network class homogeneity","Service Class","Working Class",
              "Homogeneity x Service Class","Homogeneity x Working Class")
coefgroup <- list("Social Class (ref: Intermediate class)"=2:3,"Interaction:"=4:5)
gofrow <-  list(Controls=c("Yes","Yes","Yes","Yes"))
gof1<-  c(NA,NA,"Num. countries:","Var: Group",NA)

texreg::knitreg(models)
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                  omit.coef = omitcoef,include.thresholds=FALSE,
                  custom.coef.names = coefname,
                  groups = coefgroup,custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  custom.gof.names = gof1)
```

## Interactions

```{r inter1,fig.height=5,fig.width=7,fig.cap=c("Conditional marginal effects for network class-based homogeneity on preferences for redistribution","Conditional predicted values")}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven)
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
                          as.factor = T,
                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass,
                        Q05pcm,
                        gini_disp,
                        gini_mkt,
                        rgdpna,
                        ednum,
                        female,
                        agenum,
                        country2,pi_isola,
                        # union,
                        # labst,
                        # WEIGHT
                        ) %>% 
  mutate(logrgdpna=log(rgdpna)) %>%
  # filter(!country2 %in% c("Turkey","Estonia")) %>% 
  na.omit()
# Interactions segregation x class
full_int1 <- lmer(redist~1 +female+agenum + ednum + Q05pcm + homclass*class3 +(1|country2),data=dfreg)
# Conditional Marginal effect
interplot <- 
interplot::interplot(m = full_int1,var1 = "homclass",var2="class3")
df_int <- interplot$data
df_int <- df_int[c(1,2,4),]
df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
df_int$value <- factor(df_int$value,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

df_int %>% 
ggplot() +
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  labs(caption = paste0("N=",nobs(full_int1),", Countries=",lme4::ngrps(full_int1))) +
  ylab("Class-based homogeneity coefficient")+
  xlab("Social Class")+
  ggtitle("Redistributive preferences") +
  geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(full_int1),", Countries=",lme4::ngrps(full_int1))) +  
  theme(plot.title = element_text(size = 8))

# Predicted values 
pred1<- plot_model(full_int1,type = "int")
pred_data <- data.frame(pred1$data)
pred_data <- pred_data %>% arrange(pred_data$group)
pred_data$group <- factor(pred_data$group,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

pred_data %>% 
ggplot() +
  geom_point(aes(x = x,y = predicted)) +
  geom_line(aes(x = x,y = predicted))+
  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
  facet_grid(. ~ group) +
  labs(caption = paste0("N=",nobs(full_int1),", Countries=",lme4::ngrps(full_int1))) +
  xlab("Network homogeneity")+
  ylab("Redistributive preferences") + 
  theme_minimal()
```

```{r intermacro}

```
